Price of Anarchy for Mean Field Games

### 2018-07-11 PoA.tex
hello from Christy
proposition 3

\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	When assumption $(\ref{eq:assumptions})$ is satisfied, we have the existence and uniqueness of solutions for the scalar Riccati equations associated with $u_t$, $w_t$ and $\eta_t$.

	When $r \to \infty$ we have
	\begin{equation*}
		\lambda \to \lambda^{\infty,r} := \frac{b_2}{b_2 + \bar{b}_2}
	\end{equation*}
	and
	\begin{equation*}
		B \to 0,\ B^\eta \to 0,\ C^u \to C_u^{\infty,r} := \lambda^{\infty,r}(q + \bar{q}(1-s)),\ D^{u} \to D_u^{\infty,r} := \lambda^{\infty,r}(q_T+ \bar{q}_T(1-s_T)).
	\end{equation*}
	% modification Main point 5 (nicolas)
	If $A^u \neq 0$, let $u^{\infty,r}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
	\begin{equation}
		\dot{u}^{\infty,r}_t - 2A^u u_t^{\infty,r} + C^{\infty,r}_u = 0, \qquad u_T^{\infty,r} = D^{\infty,r}_u,
	\end{equation}
	or if $A^u = 0$, let $u^{\infty,r}:[0,T] \to \mathbb{R}$ solve:
	\begin{equation}
		\dot{u}^{\infty,r}_t + C^{\infty,r}_u = 0, \qquad u_T^{\infty,r} = D^{\infty,r}_u.
	\end{equation}	
	Since assumption (\ref{eq:assumptions}) holds for arbitrarily large $r$, from the explicit formula of the solution to the scalar Riccati equation (see Appendix \ref{appendix_solving_fbsdes} equation (\ref{eq:riccati_ut_sol_app})), it is easy to show that the solution $u$ to equation (\ref{eq:riccati_ut}) converges pointwise for any $t\in[0,T]$ to the solution $u^{\infty,r}$, as $r \to \infty$. This limiting solution $u^{\infty,r}$ can be given by the following expressions: for every $t\in [0,T]$
	\begin{equation*}
	\begin{split}
	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u},\\
	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t).
	\end{split}
	\end{equation*}

	It is clear that $u^{\infty,r}$ is bounded over $[0,T]$.	Similarly, for any fixed time $t\in [0,T]$, the solutions $w_t$ and $\eta_t$ of equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) converge for each time $t\in [0,T]$ towards the solutions $w^{\infty,r}_t$ and $\eta_t^{\infty,r}$ of some first-order differential equations. Namely, for every $t\in [0,T]$,
	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}$$
	and the functions $w^{\infty,r}$ and $\eta^{\infty,r}$ are bounded over $[0,T]$.

	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, by the bounded convergence theorem we have for each $t \in [0,T]$: 
	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t,
	$$
	The limits $\bar{x}_t^{\infty,r,MFG}$ and $v_t^{\infty,r}$ are bounded over $[0,T]$. By the bounded convergence theorem, we obtain:
	\begin{equation*}
		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty,
	\end{equation*}
	and thus,
	\begin{equation*}
	\lim_{r \to \infty} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = 0.
	\end{equation*}
	It can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$. Hence,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 (\mathbb{E}(\xi))^2 \  >0.
	\end{equation*}
	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we have $\displaystyle \lim_{r \to \infty} PoA = 1$. Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
	Moreover, if
		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	then
	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
	otherwise
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

@@

hello

>>>>

% proposition r infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	When assumption $(\ref{eq:assumptions})$ is satisfied, we have the existence and uniqueness of solutions to the scalar Riccati equations associated with $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ for every given $r >0$. The superscript $r$ here indicates the dependence on this coefficient because we intend to study the behavior of these solutions in the asymptotic regime.

	When $r \to \infty$, we have
	\begin{equation*}
		\lambda^r \longrightarrow \lambda^{r\to\infty} := \frac{b_2}{b_2 + \bar{b}_2}
	\end{equation*}
	and
	\begin{equation*}
	\begin{array}{l}
		B^r \longrightarrow 0,\quad \ B^{\eta,r} \longrightarrow 0,\\
		C^{u,r} \longrightarrow C_u^{r\to \infty} := \lambda^{r \to \infty}(q + \bar{q}(1-s)),\quad \ D^{u,r} \to D_u^{r \to \infty} := \lambda^{r \to \infty}(q_T+ \bar{q}_T(1-s_T)).
	\end{array}
	\end{equation*}

	In order to show that the $PoA$ tends to $1$, we can indeed show that $\Delta SC^{r}$ tends towards $0$ while $SC^{r, MKV} >0$ in the asymptotic regime. From the equation (\ref{eq:PoA_LQ}), a sufficient condition is to demonstrate that $\int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG} )^2 dt$ is finite and the variance function $v^r_t$ is strictly positive in the asymptotic regime.\\

	% modification Main point 5 (nicolas)
	If $A^u \neq 0$, let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
	\begin{equation}
		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u,
	\end{equation}
	or if $A^u = 0$, let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ solve:
	\begin{equation}
		\dot{\left(u^{r\to \infty}_t\right)} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}	
	Since assumption (\ref{eq:assumptions}) holds for arbitrarily large $r$, from the explicit formula of the solution to the scalar Riccati equation (see Appendix \ref{appendix_solving_fbsdes} equation (\ref{eq:riccati_ut_sol_app})), it is easy to show that the solution $u^r$ to equation (\ref{eq:riccati_ut}) converges pointwise for every time $t\in [0,T]$ to the solution $u^{r \to \infty}$ as long as $r \to \infty$. This limiting solution $u^{r \to \infty}$ can be given by the following expressions: for every $t\in [0,T]$
	\begin{equation*}
	\begin{split}
	    \text{when } A^u \neq 0,\qquad & u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u},\\
	    \text{when } A^u = 0, \qquad & u_t^{r \to \infty} = D^{r \to \infty}_u + C^{r \to \infty}_u (T-t).
	\end{split}
	\end{equation*}

	From the formula (\ref{eq:riccati_ut}), we can bound the solution $u^r$ uniformly over $[0,T]$ for large enough $r$. More precisely, under assumption (\ref{eq:assumptions}), we have $B^r>0, C^{u,r}>0, D^{u,r}>0$, and $\delta^{+,r}_u > 0 > \delta^{-,r}_u$. In the asymptotic regime, we have $\lambda^{r\to \infty} >0$, $C^{r \to \infty}_u >0$ and $D^{r \to \infty}_u \geq 0$. Thus, for $r$ large enough, there exists a constant $\zeta > 0 $ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \zeta$. We also observe the following two inequalities when $A^u \neq 0$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert -(C^{u,r} + D^{u,r} \delta^{+,r}_u) + (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		=& C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		< & C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		= & C^{u,r} + D^{u,r} 2 \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		\leq&  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( \delta^{-,r}_u - D^{u,r} B^{r} ) - (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		= & D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
		\geq & \max \left\{ - \delta^{-,r}_u , \delta_u^{+,r} e^{2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
		= & \max \left\{ A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } , (-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
		\geq & \max \left\{ A^u + \vert A^u \vert, (-A^u + \vert A_u \vert) e^{-2 \sqrt{(A^u)^2 + \zeta^2} (T-t) } \right\}\\
		> & 0
	\end{IEEEeqnarray*}

	Thus, for $A^u \neq 0$, we can deduce that for $r$ large enough, for every $t \in [0,T]$
	\begin{IEEEeqnarray}{rCl}
		\vert u_t^{r} \vert  &=& \frac{\left\vert -(C^{u,r} + D^{u,r} \delta^{+,r}_u) + (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( \delta^{-,r}_u - D^{u,r} B^{r} ) - (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
		& < & \frac{ \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  }{ \max \left\{ A^u + \vert A^u \vert, (-A^u + \vert A_u \vert) e^{-2 \sqrt{(A^u)^2 + \zeta^2} (T-t) } \right\} }  \nonumber \\
		& \leq & \min \{ \kappa, \kappa e^{\kappa (T-t)} \}  \nonumber \\
		&\leq & \kappa e^{\kappa T}
	\end{IEEEeqnarray}
	where the constant $\kappa >0$ is given by
	\begin{equation}
		\kappa = \left\{
			\begin{array}{ll}
				\frac{\zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}}{A^u + \vert A^u \vert}, & if \quad A^u > 0 \\
				\max\left\{ \frac{\zeta + 2 \zeta \sqrt{(A^u)^2+ \zeta^2} }{ -A^u + \vert A_u \vert }, 2 \sqrt{ (A^u)^2 + \zeta^2 } \right\} & if \quad A^u < 0
			\end{array}
		\right.
	\end{equation}
	Thus, 
	Since $\bar{x}_t^{r,MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B^r \cdot u^r_s)ds)$,  by bounded convergence theorem we have for every $t \in [0,T]$,
	\begin{equation*}
		\bar{x}_t^{r,MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG},
	\end{equation*}
	and moreover for $r$ large enough, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $[0,T]$, i.e. 
	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}[\xi] \vert e^{ (\vert{b_1} + \vert{\bar{b}_1} + \zeta \kappa e^{\kappa T} ) T }, \quad t \in [0,T]. $$

	Similarly, for any fixed time $t\in [0,T]$, the solutions $w^r_t$ and $\eta^r_t$ of equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) converge for each time $t\in [0,T]$ towards the solutions $w^{r\to \infty}_t$ and $\eta_t^{r\to \infty}$ of some first-order differential equations. Namely, for every $t\in [0,T]$,
	$$w^r_t \xrightarrow[r \to \infty]{} w_t^{r\to \infty},\qquad \eta^r_t \xrightarrow[r \to \infty]{} \eta_t^{r\to \infty}$$
	and the functions $w^{r}$ and $\eta^{r}$ are uniformly bounded over $[0,T]$ for $r$ large enough.

	Again, by the bounded convergence theorem we have for every $t \in [0,T]$
	\begin{equation*}
	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{r\to \infty,MFG})^2 dt \  < \infty,
	\end{equation*}
	and thus
	\begin{equation*}
	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{r,MFG})^2 dt = 0.
	\end{equation*}

	%---------------------------
	Also, since $v^r_t = Var(\xi)\exp(2\int_0^t (b_1 - B^{\eta,r} \eta^r_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^{\eta,r} \eta^r_u) du) ds$, by the bounded convergence theorem we have for each $t \in [0,T]$: 
	$$	v^r_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t,
	$$
	The variance function $v_t^{r}$ is also uniformly bounded over $[0,T]$ for $r$ large enough.	It can be shown that $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV} = \frac{1}{2} \left( \int_0^T (q+\bar{q}) v^{r \to \infty}_t dt + (q_T + \bar{q}_T) v^{r\to \infty}_T + w^{r \to \infty}_0 (\mathbb{E}(\xi))^2 \right)  >0.
	\end{equation*}
	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we have $\displaystyle \lim_{r \to \infty} PoA = 1$. Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.

@@

% proposition b_2
\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
	Moreover, if
		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	then
	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
	otherwise
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

@@
